Outbreak response models of vaccine-preventable diseases in humans (1970-2019) - A systematic review

### 2023-06-21 analyses/scripts/orv_sys_rev_supplementary.Rmd
Made a table of counts of author affiliation to the location studied by disease

### Connection of authors to the studied locations 
# Foot and mouth disease

>>>>

### Connection of authors to the studied locations 
```{r}
author_location_count_by_disease <- data_without_fmd %>%
  mutate(author_in_country_studied = as_factor(author_in_country_studied), 
         disease = as_factor(disease)
         ) %>% 
  group_by(disease) %>%
  distinct(title, .keep_all = TRUE) %>% 
  count(author_in_country_studied, sort = TRUE, name = "num_of_studies") %>% 
  complete(author_in_country_studied, fill = list(num_of_studies = 0)) %>% 
  pivot_wider(names_from = author_in_country_studied, values_from = num_of_studies) %>% 
  replace_na(list(yes = 0, no = 0, not_applicable = 0)) %>% 
  mutate(total = not_applicable + no + yes) %>% 
  ungroup(disease) %>% 
  arrange(desc(total))

knitr::kable(author_location_count_by_disease,
             caption = "Author connection to the location studied by disease")
```

# Foot and mouth disease
